### 2024-05-11 thesis/chapters/appendix/A-resume.tex
Export documentation from Sphinx and Doxygen

\section{Zber vibrácií v priemysle}

@@

\section{Záver}

>>>>

\section{Zber vibrácií v priemysle}
Doteraz uplatnená metodika pre súbor údajov zaznamenaných v laboratóriu sa aplikuje na vibračných signáloch z priemyselného prostredia. Pri monitorovaní zužitkujeme mierne prispôsobený postup z noriem. Ten zahŕňa výber strojov určených na monitorovanie, identifikáciu pozícií na meranie podľa technických štandardov, predbežné merania a vývoj senzorovej jednotky.

Na zber údajov boli vyčlenené dva špirálové kompresory ako súčasť klimatizačných jednotiek pre dátové centrum a tri čerpadlá s troma elektrometrami v prečerpávacej stanici na pitnú vodu. Dlhodobejšie merania uskutočníme vlastným vnoreným systémom na báze vývojovej dosky ESP32-PoE-ISO so slotom na SD kartu. Ako senzor vibrácii použijeme MEMS akcelerometer IIS3DWB. Vyznačuje sa vysokou šírkou pásma až 6.3 kHz, nízkym šumom, a vysokou výstupným dátovým tokom 26.7 kHz cez SPI zbernicu.

@@

\section{Záver}
V diplomovej práci sme sa zamerali na výber trendových ukazovateľov pre riešenie monitorovania prevádzkového stavu a odhaľovanie porúch z vibračných signálov.  Extrahované premenné pochádzajú hlavne z popisných štatistík, z článkov o spracovaní zvukových signálov a technických noriem vibrodiagnostiky.

Dosiahnuté stratové kompresné pomery pre MaFaulDa sú 2381:1 pre všetky atribúty a 25000:1 pre šesť atribútov. Výber atribútov metódou súčinu poradí zabezpečí väčšinou najlepšiu presnosť k-NN modelu oproti metrikám samostatne. Žiadny prístup však nedokázal nájsť trojicu prediktorov s presnosťou blízkou optimálnej, ktorá je až 98\%. Trénovanie k-NN na troch hlavných komponentoch prinieslo lepšiu presnosť ako výber atribútov.

Model postupného učenia k-NN dosahuje prinajlepšom 90\% presnosť s okamžitou spätnou väzbou, 85\% so značkami oneskorenými o 250 pozorovaní a 82\% s iba 25\% anotovaného súboru údajov. Porovnateľný model trénovaný v dávkach dosahuje presnosť 98\%.

### 2024-05-11 thesis/chapters/appendix/B-technical-documentation.tex
Export documentation from Sphinx and Doxygen

\thispagestyle{empty}
\chapter{Technical documentation} \label{appendix:technical-docs}
\pagenumbering{arabic}
\renewcommand*{\thepage}{B-\arabic{page}}

% Jupyter notebooks

% Python function in package (Sphinx)

% C function of firmware

>>>>

\thispagestyle{empty}
\chapter{Technical documentation} \label{appendix:technical-docs}
\pagenumbering{arabic}
\renewcommand*{\thepage}{B-\arabic{page}}
The documentation contains a description of Jupyter Notebooks, Python package \verb|vibrodiagnostics| with utility functions for machine learning, and data logger firmware. Pages of \LaTeX \; documentation for Python were autogenerated by documentation tool \textbf{Sphinx}. Pages from C source code were created by \textbf{Doxygen}.

\section{Jupyter notebooks}
\begin{itemize}[noitemsep]

\item \textbf{cluster-dbscan.ipynb} - The clustering feasibility of the DBSCAN algorithm in the MaFaulDa dataset. Experiments to find the best epsilon parameter for complete sets of time-domain and frequency-domain features. Epsilon is estimated by localizing the knee on the curve of nearest neighbours. The method turned out to be unreliable in separating different groups of fault types. The clustering produced too many or too few samples based on the choice of minimal samples.

\item \textbf{eda-bearing-faults.ipynb} - Mark the bearing characteristic frequencies in the frequency spectrum in the axis of motion for chosen recordings from the MaFaulDa dataset, scroll compressors, water pumps, and electric motors. The bearing frequencies are calculated from coefficients or physical dimensions for the bearing designation.

\item \textbf{eda-files.ipynb} - Time-domain vibration signal waveforms are charted for acceleration values and velocity after integration. Measurements are compared between fault types or measurement positions. Statistical tests for normality and stationarity of oscillations are conducted. Comparisons from all axes for peak finding MMS algorithm, cumulative frequency spectrum, and time-frequency spectrum. Orbitals of detected fundamental frequency are shown in the spatial graph. Options are to view signals for chosen files from the MaFaulDa dataset on the inner bearing, outer bearing, or for the Pumps industrial dataset.

\item \textbf{eda-ksb-cloud.ipynb} - Overall vibration rms velocities in hourly intervals for two identical water pumps are shown in ISO severity levels. Total running time is summed from periods when each pump has been operational. Frequency spectra are also compared but are proven to have too low resolution for any conclusive result in fault recognition.

\item \textbf{eda-pumps.ipynb}
\item \textbf{eda-standing-fan.ipynb}
\item \textbf{extraction-mafaulda.ipynb}
\item \textbf{extraction-pumps.ipynb}
\item \textbf{feature-summary.ipynb}
\item \textbf{iit-src-paper.ipynb}
\item \textbf{knn-batch.ipynb}
\item \textbf{knn-mafaulda.ipynb}
\item \textbf{knn-online.ipynb}
\item \textbf{wavelets.ipynb}
\end{itemize}

\section{Data analysis package}
\includepdf[pages=3-20,scale=0.9,clip,trim=0mm 20mm 0mm 20mm,pagecommand={}]{chapters/appendix/sphinx-vibrodiagnostics}

\section{Data logger firmware}
\includepdf[pages=2-10,scale=0.9,clip,trim=0mm 20mm 0mm 20mm,pagecommand={}]{chapters/appendix/doxygen-firmware}

### 2024-05-11 thesis/chapters/appendix/C-user-guide.tex
Export documentation from Sphinx and Doxygen

\section{Data logger guide}
To measure vibrations with a data logger follow these steps:

\begin{enumerate}[noitemsep]
\item insert empty microSD card to the data logger,
\item attach the accelerometer sensor to the surface of measurement,
\item press the button and watch the LED light up,
\item when the light turns off sooner before the minute mark, the buffer was dropped, and the final file can be incomplete,
\item wait until the LED turns off, the recording is saved to file numbered sequentially from \emph{1.tsv} upwards,
\item {move files from microSD card to a separate directory e.g. \emph{abc} and run for conversion to tsv files:
\begin{lstlisting}[style=messages]
$ python bin2tsv.py abc 4
\end{lstlisting}}
\end{enumerate}

\section{Documentation guide}
Built documentation is located in directory \emph{docs} of digital medium. It can be rebuild using documentation tools \emph{Doxygen} for firmware C source code and \emph{Sphinx} for data analysis Python code. The steps of generating documentation from souce codes are as follows:

\begin{enumerate}[noitemsep]
\item {install necessary documentation tools:
\begin{lstlisting}[style=messages]
$ sudo pacman -S doxygen
$ pip install sphinx
\end{lstlisting}}
\item {rebuild the documentation using Doxygen and Sphinx:
\begin{lstlisting}[style=messages]
$ doxygen docs/firmware/doxygen.conf
$ cd docs/vibrodiagnostics
$ make html
\end{lstlisting}}
\item {View Doxygen docs in \emph{docs/firmware/html/topics.html} and Sphinx docs in \emph{docs/vibrodiagnostics/build/html/index.html}}
\end{enumerate}

>>>>

\section{Data logger guide}
To measure vibrations with a data logger follow these steps.

\begin{enumerate}[noitemsep]
\item Insert empty microSD card to the data logger.
\item Attach the accelerometer sensor to the surface of measurement.
\item Press the button and watch the LED light up.
\item When the light turns off sooner before the minute mark, the buffer was dropped, and the final file can be incomplete.
\item Wait until the LED turns off, the recording is saved to file numbered sequentially from \emph{1.tsv} upwards.
\item {Move files from microSD card to a separate directory e.g. \emph{abc} and run for conversion to tsv files:
\begin{lstlisting}[style=messages]
$ python bin2tsv.py abc 4
\end{lstlisting}}
\end{enumerate}

\section{Documentation guide}
Built documentation is located in directory \emph{docs} of the digital medium. It can be rebuild using documentation tools \emph{Doxygen} for firmware C source code and \emph{Sphinx} for data analysis Python code. The steps of generating documentation from souce codes are as follows.

\begin{enumerate}[noitemsep]
\item {Install necessary documentation tools:
\begin{lstlisting}[style=messages]
$ sudo pacman -S doxygen
$ pip install sphinx sphinx-rtd-theme sphinx_autodoc_defaultargs
\end{lstlisting}}
\item {Rebuild the documentation using Doxygen and Sphinx:
\begin{lstlisting}[style=messages]
$ doxygen docs/firmware/doxygen.conf
$ cd docs/vibrodiagnostics
$ make html
\end{lstlisting}}
\item {View Doxygen docs in \emph{docs/firmware/html/topics.html} and Sphinx docs in \emph{docs/vibrodiagnostics/build/html/index.html}}
\end{enumerate}
